MSB104_assignment1

### 2023-10-09 MSB104_assignment1.qmd
Update data 09.10.23

Sjekk DEA dataene!!!

@@

(Beskrive millioneuro i GDP)

@@

```{r}
# Since Germany contains many regions, we have deceided to present them in two new values.
# DEz1North and DEz2SOUTH are the two values where we have devided Germany in South and North. 
DEz1NORTH <- c("DE30", "DE40", "DE50", "DE60", "DE80", "DE91", "DE92", "DE93", "DE94", "DEA1", "DEA2", "DEA3", "DEA4", "DEA5", "DEE0", "DEF0", "DEG0") 
DEz2SOUTH <- c("DE11", "DE12", "DE13", "DE14", "DE21", "DE22", "DE23", "DE24", "DE25", "DE26", "DE27", "DE71", "DE72", "DE73", "DEB1", "DEB2", "DEB3", "DEC0", "DED2", "DED4", "DED5")
```

@@

```{r}
GDP_DE_nuts2 |> 
  filter(Year == 2005) |> 
  select(-Year) |> 
  st()
```

@@

>>>>

@@

@@

```{r}
# Since Germany contains many regions, we have deceided to present them in two new values.
# DEz1North and DEz2SOUTH are the two values where we have devided Germany in South and North. 
DEz1NORTH <- c("DE30", "DE40", "DE50", "DE60", "DE80", "DE91", "DE92", "DE93", "DE94", "DEA1", "DEA2", "DEA3", "DEA4", "DEA5", "DEE0", "DEF0", "DEG0") 
DEz2SOUTH <- c("DE11", "DE12", "DE13", "DE14", "DE21", "DE22", "DE23", "DE24", "DE25", "DE26", "DE27", "DE71", "DE72", "DE73", "DEB1", "DEB2", "DEB3", "DEC0", "DED2", "DED4", "DED5")
DE <- c(DEz1NORTH, DEz2SOUTH)
```

@@

@@

```{r}
Gini_stat_DE_nuts2 <- merged_temp %>%
  filter(id_nuts2 %in% DE) |> 
  group_by(Year) |> 
  summarise(
    min_Gini_each_year = min(gini_n2),
    max_Gini_each_year = max(gini_n2),
    median_Gini_each_year = median(gini_n2),
    mean_Gini_each_year = mean(gini_n2),
    sd_Gini_each_year = sd(gini_n2),
    var_Gini_each_year = sd_Gini_each_year^2
  )
```

```{r}
#| cap-location: bottom
#| fig-cap: "Gini nuts2 DE."
merged_temp |>
  filter(id_nuts2 %in% DE) |>
  ggplot(mapping = aes(
    x = Year, 
    y = gini_n2, 
    colour = id_nuts2)
    ) +
  #geom_smooth(se = FALSE, snap = 0.9)
  geom_point()
```

```{r}
# Comments 
FI <- c("FI19", "FI1B", "FI1C", "FI1D", "FI20")
```

```{r}
Gini_stat_FI_nuts2 <- merged_temp %>%
  filter(id_nuts2 %in% FI) |> 
  group_by(Year) |> 
  summarise(
    min_Gini_each_year = min(gini_n2),
    max_Gini_each_year = max(gini_n2),
    median_Gini_each_year = median(gini_n2),
    mean_Gini_each_year = mean(gini_n2),
    sd_Gini_each_year = sd(gini_n2),
    var_Gini_each_year = sd_Gini_each_year^2
  )
```

```{r}
#| cap-location: bottom
#| fig-cap: "Gini nuts2 FI."
merged_temp |>
  filter(id_nuts2 %in% FI) |>
  ggplot(mapping = aes(
    x = Year, 
    y = gini_n2, 
    colour = id_nuts2)
    ) +
  #geom_smooth(se = FALSE, snap = 0.9)
  geom_point()
```

```{r}
# Comments 
RO <- c("RO11", "RO12", "RO21", "RO22", "RO31", "RO32", "RO41", "RO42")
```

```{r}
Gini_stat_RO_nuts2 <- merged_temp %>%
  filter(id_nuts2 %in% RO) |> 
  group_by(Year) |> 
  summarise(
    min_Gini_each_year = min(gini_n2),
    max_Gini_each_year = max(gini_n2),
    median_Gini_each_year = median(gini_n2),
    mean_Gini_each_year = mean(gini_n2),
    sd_Gini_each_year = sd(gini_n2),
    var_Gini_each_year = sd_Gini_each_year^2
  )
```

```{r}
#| cap-location: bottom
#| fig-cap: "Gini nuts2 RO."
merged_temp |>
  filter(id_nuts2 %in% RO) |>
  ggplot(mapping = aes(
    x = Year, 
    y = gini_n2, 
    colour = id_nuts2)
    ) +
  #geom_smooth(se = FALSE, snap = 0.9)
  geom_point()
```
